---
title: "Virtualization - Linux Container on CentOS"
output: 
  html_document :
    theme: journal
    toc: true
    code_folding: show
    includes:
      #before_body: header.html
      after_body: footer.html
    toc_float:
      collapsed: true
      smooth_scroll: true
#flexdashboard::flex_dashboard
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(flexdashboard)
library(tint)
```

Setup {data-icon="fa-table"}
===================================== 
***



### Objective
  * Install and spin a LXC container on CentOS 7
  
  
### Pre-requisites
  * CentOS 7 64 bits -  can be downloaded as a VirtualBox image from <https://www.osboxes.org/centos/>.
  
  


 * You will need to install the EPEL repository (Exta Package For Entreprise Linux).
 
```{r class="markdown", eval = FALSE,  results = "hide"}
yum install -y epel-release
```
  
  
 * You can check if the **epel-release** repository has been added with.
 

### Install LXC

  * Now, you are ready to install LXC and its templates with: 
  
```{r class="markdown", eval = FALSE,  results = "hide"}
yum install -y lxc lxc-templates debootstrap perl libcap-devel libcgroup wget bridge-utils x-extra libvirt`
```



  * Once installation is complete, start and enable the **LXC.service**.
 

```{r class="markdown", eval = FALSE,  results = "hide"}
 systemctl start lxc
 systemctl enable lxc
```



  
    
Create a LXC container {data-icon="fa-table"}
=====================================    
***

### Explore LXC


 * You can explore the LXC directory with ` ls -lrt /usr/share/lxc/` and `ls -lrt /usr/share/lxc/templates/` where the available templates are stored.
 
    

### Create your container

  * Disable **SeLinux** with `setenforce 0`. **SeLinux** prevents the updates of some files
  
  * Create you first container by running `lxc-create -n centos_vm1 -t centos`


```{r class="markdown", eval = FALSE,  results = "hide"}
 lxc-create -n centos_vm1 -t centos
```

 * Successful creation will show this.  
 
 * List the containers created with `lxc-ls --fancy`
 

 * To update the password, run the 

```{r class="markdown", eval = FALSE, results = "hide"}
 chroot /var/lib/lxc/centos_vm1/rootfs passwd
```


### Start your container

 * Start your Centos container. 
 
```{r class="markdown", eval = FALSE, results = "hide"}
  lxc-start -n centos_vm1 -d
```
   
   `-d` will avoid being prompted the username/password fields.
 
 * You can check the `STATE` with `lxc-ls --fancy`
 

 * Now you are ready to log into your Centos container with `lxc-attach`
 
 
```{r class="markdown", eval = FALSE, results = "hide"}
  lxc-attach -n centos_vm1
```

 

Use your LXC container {data-icon="fa-table"}
=====================================    
***

 * You can then run usual commands on the container or install new packages.

```{r class="markdown", eval = FALSE, results = "hide"}
ip a s
1: lo: <LOOPBACK,UP,LOWER_UP> mtu 65536 qdisc noqueue state UNKNOWN group default qlen 1000
    link/loopback 00:00:00:00:00:00 brd 00:00:00:00:00:00
    inet 127.0.0.1/8 scope host lo
       valid_lft forever preferred_lft forever
    inet6 ::1/128 scope host
       valid_lft forever preferred_lft forever
6: eth0@if7: <BROADCAST,MULTICAST,UP,LOWER_UP> mtu 1500 qdisc noqueue state UP group default qlen 1000
    link/ether fe:5b:01:7a:f3:2c brd ff:ff:ff:ff:ff:ff link-netnsid 0
    inet 192.168.122.15/24 brd 192.168.122.255 scope global dynamic eth0
       valid_lft 3582sec preferred_lft 3582sec
    inet6 fe80::fc5b:1ff:fe7a:f32c/64 scope link
       valid_lft forever preferred_lft forever
```

```{r class="markdown", eval = FALSE, results = "hide"}
yum install -y nmap
```

  * `exit` command will allow you to exit from the container
  * `shutdown -r now` will restart the container
 